Bayesian model in JAGS

### 2023-01-16 JAGS_Bayesian_model/Jags_Bayesian_model.Rmd
comment

```{r}
basic_mod <-  "model{
 #model
  for(i in 1:n.sim){
   y[i] ~ dnorm(mu[i], tau)
   mu[i] = beta0 + beta1 * x[i]
  }

 #priors
 beta0 ~ dnorm(0, 0.01)
 beta1 ~ dnorm(0, 0.01)
 tau ~ dgamma(0.01,0.01)
 }
 "
```

@@

```{r}
############ burn-in period ############
update(jags.basic.mod,5000) # n.burnin = 1000

>>>>

```{r}
basic_mod <-  "model{
 #model
  for(i in 1:n.sim){
   y[i] ~ dnorm(mu[i], tau)
# tau is the error term

   mu[i] = beta0 + beta1 * x[i]
# beta0 and beta1 are the unknown parameters
  }

 #priors; these are weakly informative priors
 beta0 ~ dnorm(0, 0.01)
# dnorm(mean, precision)
# precision = 0.01 --> var = 100
 beta1 ~ dnorm(0, 0.01)
 tau ~ dgamma(0.01,0.01)
# dgamma(shape,rate)
 }
 "
```

@@

```{r,message=TRUE}
############ burn-in period ############
update(jags.basic.mod,5000) # n.burnin = 1000
